\chapter{Referencias}
\section{Documentación Técnica}

\begin{itemize}
	\item Django Software Foundation. (2024). \textit{Django documentation}. https://docs.djangoproject.com/en/5.1/ \cite{django-docs}
	\item Bootstrap. (2024). \textit{Bootstrap 5.3 Documentation}. https://getbootstrap.com/docs/5.3/getting-started/introduction/ \cite{bootstrap-docs}
	\item The PostgreSQL Global Development Group. (2024). \textit{PostgreSQL Documentation}. https://www.postgresql.org/docs/ \cite{postgresql-docs}
	\item Canonical Ltd. (2024). \textit{Ubuntu Documentation}. https://ubuntu.com/server/docs \cite{ubuntu-docs}
	\item Django Software Foundation. (2024). \textit{Django Email}. https://docs.djangoproject.com/en/5.1/topics/email/ \cite{django-email}
	\item Nginx, Inc. (2024). \textit{Nginx Documentation}. https://nginx.org/en/docs/ \cite{nginx-docs}
\end{itemize}
\begin{thebibliography}{{}}
\bibitem{django-docs} Django Software Foundation. (2024). Django documentation. https://docs.djangoproject.com/en/5.1/
\bibitem{bootstrap-docs} Bootstrap. (2024). Bootstrap 5.3 Documentation. https://getbootstrap.com/docs/5.3/getting-started/introduction/
\bibitem{postgresql-docs} The PostgreSQL Global Development Group. (2024). PostgreSQL Documentation. https://www.postgresql.org/docs/
\bibitem{ubuntu-docs} Canonical Ltd. (2024). Ubuntu Documentation. https://ubuntu.com/server/docs
\bibitem{django-email} Django Software Foundation. (2024). Django Email. https://docs.djangoproject.com/en/5.1/topics/email/
\bibitem{nginx-docs} Nginx, Inc. (2024). Nginx Documentation. https://nginx.org/en/docs/
\end{thebibliography}
\section{Recursos Académicos}
